SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-20 paper/bio_MTedit.tex
asd

If a VTS is $k$-connected, every pair of compartments remain reachable after dropping $k-1$ vesicles. In principle the connectivity of a VTS can be determined by cell-biological studies.
% We have previously shown \cite{shukla} that a feasible VTS must be at least 3-connected but might need to have higher connectivity. 
Here we have build a tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
%We later will discuss conditions of maximum connectivity [or LGC, least guarantee connectivity] and minimal connectivity [or LRC, least required connectivity].

>>>>

\ankit{If a VTS is $k$-connected, every pair of compartments remain reachable after dropping $k-1$ vesicles. In principle the connectivity of a VTS can be determined by cell-biological studies.}
% We have previously shown \cite{shukla} that a feasible VTS must be at least 3-connected but might need to have higher connectivity. 
Here we have build a tool that studies properties of VTSs that are not $k$-connected, from some $k$. 
%We later will discuss conditions of maximum connectivity [or LGC, least guarantee connectivity] and minimal connectivity [or LRC, least required connectivity].
